Signatures of Foreground Sky in Power Spectra of Redshifted Neutral Hydrogen from the Epoch of Reionization

### 2014-09-11 foreground_delay_spectrum_modeling.tex
From v0.5: =========
(*) Added an entry to Sullivan et al.(2012) in the eor.bib file and cited this
reference in the tex file.
(*) Updated figures
(*) Removed empty appendix

The data are flagged\footnote{\url{http://sourceforge.net/p/aoflagger}} for interference \citep{off12,off10}, removing 3\% of the data and averaged in time  and frequency from the raw 0.5~s, 40~kHz to 2s, 80~kHz. These data are then calibrated to a simulation of the sky containing 2420 point--like objects selected from the MWA Commissioning Survey (MWACS; Hurley-Walker et al, in prep). MWACS was compiled using observations taken with subsets of the array during the final buildout and commissioning. It has a flux density limit of 25~mJy and a declination range of -12\arcdeg to -40\arcdeg evenly covering the field of view of the observations reported here. The objects used in calibration are selected to lie inside the 5\% contour of the primary lobe of the tile power--pattern. The calibration algorithm computes complex gain solutions per channel per antenna averaged to two minute intervals. The solutions are still fairly low signal--to--noise so we iteratively project along the antenna and frequency dimensions to capture the relatively independent passband and antenna--to--antenna variation. First, we average the channel gains over all antenna to obtain a high signal--to--noise measurement of the bandpass. After applying this single passband, we do a second round of calibration and fit second and first order polynomials for amplitude and phase respectively for each antenna. This flattens any residual variation in bandpass and removes small phase slopes due to variation in cable delay. Finally, we fit for an additional phase known to be caused by reflection in 150~m length cables. %possibly could add elaboration, if I knew exactly which version of the cal was done here. doesn't really matter

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/delta_array_3_baseline_comparison_visibilities_0.3m_ground_custom_gaussian_FG_model_csm_all_sky_nside_64_Tsys_90.0K_185.0_MHz_30.7_MHz_bnw2.0.eps}
\caption{Absolute value of delay spectrum, $|V_\eta(\overline{\mathbf{x}},\eta)|$, for three chosen antenna spacings of length: $\sim$84~m ({\it top}), $\sim$105~m ({\it middle}), and $\sim$170~m ({\it bottom}). The antenna spacing vector is specified in each panel along East, North and Upward directions. The dotted, dashed and solid lines denote contributions from diffuse emission, compact objects and composite foreground model respectively. The dot--dashed lines mark the horizon delay limits. The shaded region denotes the envelope of uncertainty around expected values for composite model. This uncertainty is dictated by uncertainties in spectral indices of foreground models inside the delay horizon delay limits. Outside the horizon delay limits, it is predominantly due to thermal noise. Compact objects dominate the central regions of power spectrum while both components, especially diffuse emission on short antenna spacings, dominate near the horizon delay limits, giving rise to a {\it pitchfork}--shaped structure. \label{fig:pitchfork-baselines}}
\end{figure}

@@

\appendix

>>>>

The data are flagged\footnote{\url{http://sourceforge.net/p/aoflagger}} for interference \citep{off12,off10}, removing 3\% of the data and averaged in time  and frequency from the raw 0.5~s, 40~kHz to 2s, 80~kHz. These data are then calibrated to a simulation of the sky containing 2420 point--like objects selected from the MWA Commissioning Survey (MWACS; Hurley-Walker et al, in prep). MWACS was compiled using observations taken with subsets of the array during the final buildout and commissioning. It has a flux density limit of 25~mJy and a declination range of -12\arcdeg to -40\arcdeg evenly covering the field of view of the observations reported here. The objects used in calibration are selected to lie inside the 5\% contour of the primary lobe of the tile power--pattern. The calibration algorithm \citep{sul12} computes complex gain solutions per channel per antenna averaged to two minute intervals. The solutions are still fairly low signal--to--noise so we iteratively project along the antenna and frequency dimensions to capture the relatively independent passband and antenna--to--antenna variation. First, we average the channel gains over all antenna to obtain a high signal--to--noise measurement of the bandpass. After applying this single passband, we do a second round of calibration and fit second and first order polynomials for amplitude and phase respectively for each antenna. This flattens any residual variation in bandpass and removes small phase slopes due to variation in cable delay. Finally, we fit for an additional phase known to be caused by reflection in 150~m length cables. %possibly could add elaboration, if I knew exactly which version of the cal was done here. doesn't really matter

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/delta_array_3_baseline_comparison_visibilities_0.3m_ground_custom_gaussian_FG_model_all_sky_nside_64_Tsys_90.0K_185.0_MHz_30.7_MHz_bnw2.0.eps}
\caption{Absolute value of delay spectrum, $|V_\eta(\overline{\mathbf{x}},\eta)|$, for three chosen antenna spacings of length: $\sim$84~m ({\it top}), $\sim$105~m ({\it middle}), and $\sim$170~m ({\it bottom}). The antenna spacing vector is specified in each panel along East, North and Upward directions. The dotted, dashed and solid lines denote contributions from diffuse emission, compact objects and composite foreground model respectively. The dot--dashed lines mark the horizon delay limits. The shaded region denotes the envelope of uncertainty around expected values for composite model. This uncertainty is dictated by uncertainties in spectral indices of foreground models inside the delay horizon delay limits. Outside the horizon delay limits, it is predominantly due to thermal noise. Compact objects dominate the central regions of power spectrum while both components, especially diffuse emission on short antenna spacings, dominate near the horizon delay limits, giving rise to a {\it pitchfork}--shaped structure. \label{fig:pitchfork-baselines}}
\end{figure}

@@
